---
title: "Healthcare"
author: "Tori Green"
date: "11/27/2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(readxl)
hospital1 <- read_excel("~/Desktop/Simplilearn/Data Science with R/1555054100_hospitalcosts (1).xlsx")
```


#View the structure of the dataset
```{r}
str(hospital1)
```

#View the first few rows of dataset
```{r}
head(hospital1)
```

#Descriptive statistics of each variable.
```{r}
summary(hospital1)
```


```{r}
library(psych)
describe(hospital1)
```

# 1.1 Mean total hospital discharge costs by age
```{r}
library(tidyverse)
data2 <-hospital1  %>%
    group_by(AGE) %>%
    summarise(
        n = n(),
        mean_tc = mean(TOTCHG, na.rm=T))
print(data2)
```



#Graph 1.1 Total Costs (Mean Value) By Age of Patient
```{r}
library(ggplot2)
ggplot(data = data2, aes(x=AGE, y= mean_tc)) +geom_bar(stat = "identity", position="dodge") + scale_y_continuous(limits = c(0,12000)) +coord_flip()
```

#1.2 Median total hospital discharge costs by age
```{r}
data1 <-hospital1  %>%
    group_by(AGE) %>%
    summarise(
        n = n(),
        med_tc = median(TOTCHG, na.rm=T))
print(data1)
```

#Graph 1.2 Total Costs (Median Value) By Age of Patient
```{r}
library(ggplot2)
ggplot(data = data1, aes(x=AGE, y= med_tc)) +geom_bar(stat = "identity", position="dodge") + scale_y_continuous(limits = c(0,12000)) +coord_flip()
```

#1.3 Total Costs (Total Sum) By Age of Patient
```{r}
data3 <-hospital1  %>%
    group_by(AGE) %>%
    summarise(
        n = n(),
        sum_tc = sum(TOTCHG, na.rm=T))
print(data3)
```

#Graph 1.3 Total Costs (Total Sum) By Age of Patient
```{r}
library(ggplot2)
ggplot(data = data3, aes(x=AGE, y= sum_tc)) +geom_bar(stat = "identity", position="dodge") + scale_y_continuous(limits = c(0,680000)) +coord_flip()
```
# #2

#2 Diagnosis-related group that has maximum average total hospital cost
```{r}
totdata1 <-hospital1  %>%
    group_by(APRDRG) %>%
    summarise(
        n = n(),
        mean_tcexp = mean(TOTCHG, na.rm=T))
# Sort by mean_tcexp
data.frame(totdata1)
totdata1[order(-totdata1$mean_tcexp),]
```


#2.2 Diagnosis-related group that has maximum hospitalization
```{r}
losdata1 <-hospital1  %>%
    group_by(APRDRG) %>%
    summarise(
        n = n(),
        mean_los = mean(LOS, na.rm=T))
# Sort by mean_los
data.frame(losdata1)
losdata1[order(-losdata1$mean_los),]
```
# #3

#3.1
#Create the scatter plot with `RACE` on the x-axis and `TOTCHG` on the y-axis
#Add a regression linew ith the form `abline(lm(y ~ x))`
```{r}
plot(hospital1$RACE, hospital1$TOTCHG)
abline (lm(hospital1$TOTCHG ~ hospital1$RACE))
```

#3.2 Calculate the correlation between RACE AND TOTCHG
```{r}
cor(hospital1$TOTCHG, hospital1$RACE)
```


#3.3 Linear regression modeling for race and total charge
```{r}
lrRACE <-lm(TOTCHG ~ RACE, data=hospital1)
summary(lrRACE)
```
# #4

#4.1 Determine the correlation among each of the variables.
```{r}
cor_data <- hospital1[,1:length(hospital1)]
round(cor(cor_data),2)

```


#4.2 Multiple Regression with total costs as the dependent variable and Age + Gender as the independent variables
```{r}
lr4 <-lm(TOTCHG ~ AGE + FEMALE, data=hospital1)
summary(lr4)
```


#Table 4.1 Mean of total charges subset by age and gender
```{r}
data4 <-hospital1  %>%
    group_by(AGE,FEMALE) %>%
    summarise(
        n = n(),
        mean_agegen = mean(TOTCHG, na.rm=T))
print(data4)
```

#Graph 4.1 Mean of total charges subset by age and gender 
```{r}
library(ggplot2)
ggplot(data = data4, aes(x=AGE, y= mean_agegen, fill = FEMALE)) +geom_bar(stat = "identity", position="dodge") + scale_y_continuous(limits = c(0,12000)) +coord_flip()
```
# #5


#5 Multiple linear regression with age, gender, and race as the independent/explanatory variables and length of stay as the dependent/response variable.
```{r}
model <- lm(LOS ~ AGE + FEMALE + RACE, data = hospital1)
summary(model)
```
# #6

#Model 6a. Multiple Regression Analysis with total charge as the dependent/response variable and the remaining variables as the independent or explanatory variables
```{r}
model6a <- lm(TOTCHG ~ AGE + FEMALE + RACE + LOS + APRDRG, data = hospital1)
summary(model6a)
```

#Figure 6.1 Relative Importance of Explanatory Variables
```{r}
library(relaimpo)
hospri = calc.relimp(model6a)
print(hospri)
```
#Graph 6.1 for Figure 6.1
```{r}
barplot(hospri$lmg, ylab="Relative Importance", xlab="Variable", main = "Relative Importance of Explanatory Variables")
```


#6 Determine which variable mainly affects total costs.
#Figure 6.2 Relative Importance of Explanatory Variables (Total sums to 100)
```{r}
hospri2 = calc.relimp(model6a, rela = TRUE)
print(hospri2)

```

#Graph 6.2 for Figure 6.2
```{r}
barplot(hospri2$lmg, ylab="Relative Importance", xlab="Variable", main = "Relative Importance of Explanatory Variables")
```




